MSA Asthma Place of Service Timeseries

### 2018-08-12 r_scripts/analysis/msa_asthma_timeseries.Rmd
deleted useless slot.
updated something.

```{r load_data}
# load asthma casecross place of service list
load("../../data/health/asthma_cc_pos_list.RData")
# extract names
vars_keep <- names(asthma_cc_pos_list[[4]])
```

@@

```{r}

>>>>

```{r load_data}
# load asthma casecross place of service list
load("./data/health/asthma_cc_pos_list.RData")
# extract names
vars_keep <- names(asthma_cc_pos_list[[4]])
```

@@
